A community-maintained standard library of population genetic simulations

### 2019-12-19 popSimManu.tex
Edit pass on intro.

\section*{Introduction}
While population genetics has always used statistical methods to make inferences from data,
the degree of sophistication of the questions, models, data, and computational approaches
used have all increased over the past decade. Currently there exist myriad computational methods
that can infer the histories of populations
\citep{gutenkunst2009inferring,li2011inference,excoffier2013robust,schiffels2014inferring, terhorst2017robust,ragsdale2019models},
the distribution of fitness effects \citep{Boyko:2008cr,kim2017inference,tataru2017inference,Fortier703918,Huang2019,Vecchyo770966},
recombination rates \citep{chan2012genome,lin2013fast,Adrion662247,Barroso2019},
and the extent of positive selection in genome sequence data
\citep{eyre2009estimating, alachiotis2012omegaplus,degiorgio2016sweepfinder2,kern2018diplos,sugden2018localization}.
While en masse these methods have increased our understanding of the
impacts of genetic and evolutionary processes, very little has been done to systematically
benchmark the quality of inferences gleaned from computational population genetics.
As large databases of population genetic variation begin to be used to inform public health procedures,
the accuracy and quality of these inferences is becoming even more important.
Assessing accuracy in population genetics is challenging in large part because
 ``ground-truth'' in population genetics comes from simulation,
not from empirical observations, and as a field there has been no agreement as to what should
constitute community standards or best practices. The general modus operandi to date has been to
introduce methods that are validated by a set of bespoke simulations produced by individual
groups. Beyond inefficiency from duplicated effort, such a situation leads
to decreased reproducibility and transparency across the entire field.
Here we describe \stdpopsim, a community-driven catalog
of standardized population genetics models spanning a variety of common study organisms.
This resource will empower the field to rigorously evaluate population genetic software
and select the best tool for a given task, thereby substantially increasing the reliability of population genetic inferences.
%DRS: still not in love with this last sentence here, but tried to make it a little less sappy by adding some explanation.
%ADK: made some edits here
%RNG: Removed the sap. :-P Feel free to put it back if you like it better.

@@

The software has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its accuracy.
Importantly, we have rigorous quality control methods to ensure implemented models are accurate
and have documented methods for others to contribute new modules.
We invite new collaborators to join our community.
Below we describe the resource and give
examples of how it can be used to benchmark demographic inference methods.

>>>>

\section*{Introduction}
While population genetics has always used statistical methods to make inferences from data,
the degree of sophistication of the questions, models, data, and computational approaches
used have all increased over the past decade. Currently there exist myriad computational methods
that can infer the histories of populations
\citep{gutenkunst2009inferring,li2011inference,excoffier2013robust,schiffels2014inferring, terhorst2017robust,ragsdale2019models},
the distribution of fitness effects \citep{Boyko:2008cr,kim2017inference,tataru2017inference,Fortier703918,Huang2019,Vecchyo770966},
recombination rates \citep{chan2012genome,lin2013fast,Adrion662247,Barroso2019},
and the extent of positive selection in genome sequence data
\citep{eyre2009estimating, alachiotis2012omegaplus,degiorgio2016sweepfinder2,kern2018diplos,sugden2018localization}.
While these methods have increased our understanding of the
impacts of genetic and evolutionary processes, very little has been done to systematically
benchmark the quality of inferences gleaned from computational population genetics.
As large databases of population genetic variation begin to be used to inform public health procedures,
the accuracy and quality of these inferences is becoming ever more important.
Assessing accuracy in population genetics is challenging in large part because
 ``ground-truth'' in population genetics comes from simulation,
not from empirical observations, and as a field there has been no agreement
on community standards or best practices. The general modus operandi to date has been to
introduce methods that are validated by a set of bespoke simulations produced by individual
groups. Beyond inefficiency from duplicated effort, such a situation leads
to decreased reproducibility and transparency across the entire field.
Here we describe \stdpopsim, a community-driven catalog
of standardized population genetics models spanning a variety of common study organisms.
This resource will empower the field to rigorously evaluate population genetic software,
%and select the best tool for a given task,
thereby substantially increasing the reliability of population genetic inferences.
%DRS: still not in love with this last sentence here, but tried to make it a little less sappy by adding some explanation.
%ADK: made some edits here
%RNG: Removed the sap. :-P Feel free to put it back if you like it better.
%JK: not crazy about it either. Making it shorter helps though?

@@

The software has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its quality.
Importantly, we have rigorous quality control methods to ensure implemented models are accurate
and have documented methods for others to contribute new modules.
We invite new collaborators to join our community.
Below we describe the resource and give
examples of how it can be used to benchmark demographic inference methods.
